---
title: "Meta analysis"
format: html
editor: visual
---

```{r}
library(here)
library(tidyverse)
```

```{r}
df <- read_csv(here('data', 'update_temperature.csv'))
```

I have 2 questions I am considering:

1. Are countries with a higher renewable energy percentage less affected by extreme weather events? 
response: Extreme_Weather_Events - # of recorded extreme weather events 
predictor: Renewable_Energy_pct - renewable energy consumption

```{r}
df |>
  ggplot(aes(x = Renewable_Energy_pct, y = Extreme_Weather_Events)) +
  geom_point(color = "tan1") +
  geom_smooth(aes(linetype = "Regression line"), method = "lm", se = FALSE, color = "black") +
  labs(
    title = "Renewable Energy Use and Extreme Weather",
    x = "Renewable Energy Use (%)",
    y = "Extreme Weather Events"
  ) +
  theme_minimal()
```


2. Do countries that maintain or increase their forest area experience fewer weather disasters over time?
response: Extreme_Weather_Events - # of recorded extreme weather events 
predictor: Forest_Area_pct -  percentage of land covered by forests


```{r}
df |>
  ggplot(aes(x = Forest_Area_pct, y = Extreme_Weather_Events)) +
  geom_point(color = "tan1") +
  geom_smooth(aes(linetype = "Regression line"), method = "lm", se = FALSE, color = "black") +
  labs(
    title = "Land Covered by Forests Percentage and Extreme Weather",
    x = "Percentage of Land Covered by Forests",
    y = "Extreme Weather Events"
  ) +
  theme_minimal()
```





